PS753 Glossary

### 2022-01-30 _academics/ps753-glossary/ps753-glossary.Rmd
Add Lazer terms

node / ego / actor
: $i$ - the node being discussed or focused on; @hanneman also note "Actors are described by their relations, not by their attributes."

@@

>>>>

node / ego / actor
: $i$ - the node being discussed or focused on; also note "Actors are described by their relations, not by their attributes."^[@hanneman]

@@

### @lazer2011

homophily
: the idea that individuals who are similar to one another are more likely to form ties

whole network data
: relational information about a whole set (or subset) of data, with all of the actors' relations to each other considered

egocentric data
: relational information about a set of nodes connected to one particular node and not to each other

diameter
: the maximum degree of separation between any two nodes in the network

one-mode data
: ties among one set (or category) of agent, such as nations in the context of trade

two-mode data
: ties between different sets (or categories) of agents, such as ties between nations and international organizations
